Kindly Bent to Free Us

### 2019-06-19 kindly/infer/infer.tex
Prepare.

We reformulate the HM(X) type inference in the context of our affine type
system. The main difference compared to HM(X) are noted in \addlin{blue}.
We note $\inferW{\addlin{\Sigma}}{(C,\unif)}{\bf{\E}}{\bf{e}}{\tau}$ when
$e$\ as type $\tau$ in $\E$ under the constraints $C$ and unifier $\unif$.
$\Sigma$ is a map which associates free variables in $e$ to
their kinds.
As before, $\E$ and $e$ are the input parameters of the inference
algorithm. The syntax-directed rules are shown in \cref{rules:typing}.

@@

The normalization procedure is noted $\normalize{C_0}{\unif_0}$ where
$C_0\in \CL$ is a set of constraints and $\unif_0$ is a substitution.
It returns a constraint $C \in \mathcal S$ in
solved form and a unifier $\unif$.
The main idea of the algorithm is to first remove all the type equalities
by using regular Herbrand unification. After that, we only have
a set of inequalities among kinds, which we can consider as a relation.
We can then saturate the relation,
unify all kinds that in the same equivalence classes to obtain
a most general unifier on kind variables,
remove all existentially quantified variables and
then minimize back the relation.

>>>>

We reformulate the HM(X) type inference in the context of our affine type
system. The main difference compared to HM(X) are noted in \addlin{blue}.
We note $\inferW{\addlin{\Sigma}}{(C,\unif)}{\bf{\E}}{\bf{e}}{\tau}$ when
$e$\ has type $\tau$ in $\E$ under the constraints $C$ and unifier $\unif$.
$\Sigma$ is a map which associates free variables in $e$ to
their kinds.
As before, $\E$ and $e$ are the input parameters of the inference
algorithm. The syntax-directed rules are shown in \cref{rules:typing}.

@@

The normalization procedure is noted $\normalize{C_0}{\unif_0}$ where
$C_0\in \CL$ is a set of constraints and $\unif_0$ is a substitution.
It returns a constraint $C \in \mathcal S$ in
solved form and a unifier $\unif$.
The main idea of the algorithm is to first remove all the type equalities
by using regular Herbrand unification. After that, we only have
a set of inequalities among kinds, which we can consider as a relation.
We can then saturate the relation,
unify all kinds that are in the same equivalence classes to obtain
a most general unifier on kind variables,
remove all existentially quantified variables and
then minimize back the relation.
